

---
title: "Supplementary Information: Models"
author: "Laura Geronimo"
output:
  html_document:
    toc: true
    toc_depth: 6
    theme: united

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
##Libraries

library(ggplot2)
library(dplyr)
library(caret)

library(pacman)
library(stringr)

library(Hmisc)
library(tidycensus)
library(tidyverse)
library(corrplot)
library(data.table)
library(pastecs)
library(car)
library(gvlma)
library(qcc)
library(stargazer)

library(forcats)
library(boot)
library(bootstrap)
library(fixest)
library(lmtest)
library(sandwich)
library(cowplot)

library(pROC)
library(MASS)

library(SSVS)


options (scipen=999)

#importing data
DNZV1 <- read.csv('C:/Users/lgero/Box/Research/FEMA_project/Data/Edited/HMA/DNZLevel/DNZ_V1/DNZV1_unLev.csv')
names(DNZV1)
DNZV1_shore  <- subset(DNZV1, ZCTA_shore==1)
table(DNZV1_shore$p2state)

DNZV1_shore <- subset(DNZV1_shore, p2state!="Illinois" &
                         p2state!="Indiana" & 
                         p2state!="Kentucky" & 
                         p2state!="Ohio" &
                         p2state!="West Virginia")

```

## Examining for outliers
```{r include=FALSE}
plot(DNZV1_shore$felev, DNZV1_shore$MHVadj_W_100k)
plot(DNZV1_shore$felev, DNZV1_shore$fWhite)
plot(DNZV1_shore$felev, DNZV1_shore$NFIP_ICCadj_YOLZ_W_1M)
plot(DNZV1_shore$felev, DNZV1_shore$count_fema_sfha_W_1k)


```

## Full Sample Variable Selection Procedure


### M0 Stepwise regression on all variables

Here I add all variables to the regression model and then apply stepwise AIC to see what variables are selected 
```{r include = FALSE}
M0_all <- glm(felev~
                TotPop_W_10k +
                PopDense_W_1k +
                fWhite +
                fBlack +
                fHisp +
                MHIadj_W_10k +
                MHVadj_W_100k +
                TotOccHU_W_10k +
                TotHU_W_10k +
                RepRate +
                #mrp_ideology1 +
                fOwnOcc +
                fRentOcc +
                TaxBaseEst_1B_W +
                count_fema_sfha_W_1k +
                NFIP_AllClaimsAdj_YOLZ +
                NFIP_ICCadj_YOLZ_W_1M +
                IHP_fldDamAmountAdjDNZ_W_10M +
                Hurricane +
                factor(StateNumLG) +
                factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(M0_all)

#note: this takes processing time
stepwise_M0_all <- stepAIC(M0_all, direction = "both") #this selects the model with the lowest AIC
summary(stepwise_M0_all)

```

### SVSS test
Running SVSS test to see which variables are included
```{r include = FALSE}
outcome <- "felev"
predictors <- c("TotPop_W_10k",
                   "PopDense_W_1k",
                   "fWhite",
                   "fBlack",
                   "fHisp",
                   "MHIadj_W_10k",
                   "MHVadj_W_100k",
                   "TotOccHU_W_10k",
                   "TotHU_W_10k",
                   "RepRate",
                   "mrp_ideology1",
                   "fOwnOcc",
                   "fRentOcc",
                   "TaxBaseEst_1B_W",
                   "count_fema_sfha_W_1k",
                   "NFIP_AllClaimsAdj_YOLZ", 
                   "NFIP_ICCadj_YOLZ_W_1M",
                   "IHP_fldDamAmountAdjDNZ_W_10M",
                   "Hurricane",                  
                   "fyDeclared",
                   "StateNumLG")


svss_fs_allvars <- ssvs(data=DNZV1_shore,
     y=outcome,
     x=predictors,
     continuous = FALSE,
     inprob=0.5,
     runs=1000,
     burn=500)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
plot(svss_fs_allvars)

```


### Correlation Matrices on select vars
Note that in preparation for modeling, we examine all of the variables recommended in the SVSS test, plus variables that were significant in the Chi-Square and Anova tests, and are relevant to the literature based on domain knowledge. 

```{r include=FALSE}
fs_vars_V1 <- DNZV1_shore[,c("TotPop_W_10k",    #ANOVA, 
                       "PopDense_W_1k",         #Stepwise
                       "fWhite",                #ANOVA, Stepwise
                       "fHisp",                 #ANOVA, stepwise, SVSS
                       "MHIadj_W_10k",          #stepwise
                       "MHVadj_W_100k",         #ANOVA, stepwise, SVSS
                       "TotOccHU_W_10k",        #ANOVA, stepwise, SVSS
                       "TotHU_W_10k",           #ANOVA, stepwise
                       "mrp_ideology1",          #ANOVA, stepwise
                       "fOwnOcc",               #ANOVA
                       "fRentOcc",              #ANOVA
                       "TaxBaseEst_1B_W",       #stepwise
                       "count_fema_sfha_W_1k",  #ANOVA, stepwise, svss
                       "NFIP_ICCadj_YOLZ_W_1M", #ANOVA, stepwise, svss
                       "Hurricane")]            #ANOVA, SVSS        

cor_fullSample <- cor(fs_vars_V1[,sapply(fs_vars_V1, is.numeric)])
print(cor_fullSample)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
corrplot(cor_fullSample, method = "circle")
corrplot(cor_fullSample,method="color", type="lower",
         addCoef.col = "black" , 
         number.cex= 0.50, 
         tl.cex=0.50, tl.col="black")
```




##Stepwise Regression 

## Model 1: All hypotheses


##### Correlation Matrices for M1

```{r include=FALSE}
fs_vars_V1 <- DNZV1_shore[,c(#"TotPop_W_10k",    #ANOVA, Stepwis
                       "PopDense_W_1k",         #Stepwise
                       "fWhite",                #ANOVA, Stepwise
                       #"fHisp",                 #ANOVA, stepwise, SVSS
                       #"MHIadj_W_10k",          #stepwise
                       "MHVadj_W_100k",         #ANOVA, stepwise, SVSS
                       #"TotOccHU_W_10k",        #ANOVA, stepwise, SVSS
                       #"TotHU_W_10k",           #ANOVA, stepwise
                       #"mrp_ideology1",          #ANOVA, stepwise
                       #"TaxBaseEst_1B_W",       #stepwise
                       "count_fema_sfha_W_1k",  #ANOVA, stepwise, svss
                       "NFIP_ICCadj_YOLZ_W_1M", #ANOVA, stepwise, svss
                       "Hurricane")]            #ANOVA, SVSS 

cor_fullSample <- cor(fs_vars_V1[,sapply(fs_vars_V1, is.numeric)])
print(cor_fullSample)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
corrplot(cor_fullSample, method = "circle")
corrplot(cor_fullSample,method="color", type="lower",
         addCoef.col = "black" , 
         number.cex= 0.50, 
         tl.cex=0.50, tl.col="black")
```

Based on analysis of the correlation matrix, we retain all variables. Next we run a model without Fixed effects and check the VIF scores. 

##### M1 - Full model without fixed effects & select vars -checking VIF
```{r include=FALSE}
# Full model without fixed effects (fe)
M1 <- glm(felev ~  
             MHVadj_W_100k +
             fWhite+
             #mrp_ideology1 +
             Hurricane + 
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
             PopDense_W_1k, 
           data = DNZV1_shore, family = binomial)


##testing for overdispersion
deviance(M1)/df.residual(M1) #

```

###### VIF
```{r echo=FALSE, message=FALSE, warning=FALSE}
##testing for multicollinearity
M1_Vif <- car::vif(M1) #
M1_Vif #GOOD

```

The results of the VIF suggest that all of these variables are ok to include for M1. Now adding fixed effects, as well as an interaction term on fWhite and MHV. Then we run the stepwise procedure to select the final model.

##GOT HERE ####

#####  M1 - Full model with fixed effects & select vars
```{r include=FALSE}
# Full model with all predictors
M1 <- glm(felev ~  
             MHVadj_W_100k +
             fWhite+
             MHVadj_W_100k*fWhite +
             #mrp_ideology1 +
             Hurricane + 
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
             #PopDense_W_1k +
             TotPop_W_10k +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)
summary(M1)

#testing for overdispersion
deviance(M1)/df.residual(M1) #

##testing for multicollinearity
M1_Vif <- car::vif(M1) #Note - includes FE
M1_Vif

#exponentiating coeff for odds ratios
M1_Exp <- M1
M1_Exp$coefficients <- exp(M1_Exp$coefficients)
M1_Exp

# pseudo R-squared
R1 <- (1-(M1$deviance)/(M1$null.deviance))
R1 <- round(R1,2)
R1

##Model Viz
V1 <- stargazer(M1,
                type="html",
                omit=c("StateNumLG","fyDeclared"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison", 
                dep.var.labels = c("Ratio of felev"),
                add.lines = list(c("State FE","Yes"),
                                 c("Year FE", "Yes"),
                                 c("Pseudo $R2$", R1)),
                digits=2,
                column.sep.width = "10pt",
                #order=order,
                single.row = FALSE,
                align=TRUE,
                out="C:/Users/lgero/Box/Research/FEMA_project/Results/myHMA10/DNZ_V1/felev/zs_M1_fe.htm")
```




###Running stepwise to obtain final model for analysis
```{R include=FALSE}
M1_SW <- stepAIC(M1, direction = "both")  
summary(M1_SW)

```

The stepwise procedure identifies a model that includes 4 variablesand fixed effects.

Note that the stepwise model drops variables of interest like race, political ideology, and controls like population density. 

##### M1_SW: M1 stepwise model & diagnostics
```{r include= FALSE}
M1_SW <- glm(felev ~  
             MHVadj_W_100k +
             #mrp_ideology1 +
             fWhite +
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)
summary(M1_SW)

##testing for overdispersion
deviance(M1_SW)/df.residual(M1_SW) #

##testing for multicollinearity
M1_SW_Vif <- car::vif(M1_SW) #Note - includes FE
M1_SW_Vif

#exponentiating coeff for odds ratios
M1_SW_Exp <- M1_SW
M1_SW_Exp$coefficients <- exp(M1_SW_Exp$coefficients)
M1_SW_Exp

# pseudo R-squared
R1 <- (1-(M1_SW$deviance)/(M1_SW$null.deviance))
R1 <- round(R1,2)
R1

##Model Viz
V1 <- stargazer(M1_SW,
                type="html",
                omit=c("StateNumLG","fyDeclared"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison", 
                dep.var.labels = c("Ratio of felev"),
                add.lines = list(c("State FE","Yes"),
                                 c("Year FE", "Yes"),
                                 c("Pseudo $R2$", R1)),
                digits=2,
                column.sep.width = "10pt",
                #order=order,
                single.row = FALSE,
                align=TRUE,
                out="C:/Users/lgero/Box/Research/FEMA_project/Results/myHMA10/DNZ_V1/felev/zs_M1SW_fe.htm")



```

```{r echo=FALSE, results= 'asis'}
stargazer(M1_SW,
                type="html",
                omit=c("fyDeclared", "StateNumLG"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model 1B: Full sample (testing Race and MHV", 
                dep.var.labels = c("odds Ratio of felev"),
                add.lines = list(c("State FE","YES"),
                                 c("Year FE", "YES"),
                                 c("Pseudo $R2$", R1)),
                covariate.labels = c("MHV ($100k W)",
                                     "Fraction White",
                                     "Count of HUs in FEMA SFHA 1k (W)",
                                     "NFIP ICC Claims 1M (W) by ZCTA-YOL"),
                digits=2,
                column.sep.width = "10pt",
                single.row = FALSE,
                align=TRUE)
```


##### M1 Series A.0: Single variable model all explanatory vars, with Fixed Effects:
```{r include= FALSE}

##M0: FE 
names(DNZV1_shore)
M0 <- glm(felev~
            factor(StateNumLG) +
            factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(M0)

##testing for overdispersion
deviance(M0)/df.residual(M0)

##testing for multicollinearity
M0_Vif <- car::vif(M0) 
M0_Vif

#exponentiating coeff for odds ratios
M0Exp <- M0
M0Exp$coefficients <- exp(M0Exp$coefficients)
M0Exp

# pseudo R-squared
R0 <- (1-(M0$deviance)/(M0$null.deviance))
R0 <- round(R0,2)
R0


##M1: MHV
names(DNZV1_shore)
M1 <- glm(felev~
            MHVadj_W_100k +
            factor(StateNumLG) +
            factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(M1)

##testing for overdispersion
deviance(M1)/df.residual(M1)

##testing for multicollinearity
M1_Vif <- car::vif(M1) 
M1_Vif

#exponentiating coeff for odds ratios
M1Exp <- M1
M1Exp$coefficients <- exp(M1Exp$coefficients)
M1Exp

# pseudo R-squared
R1 <- (1-(M1$deviance)/(M1$null.deviance))
R1 <- round(R1,2)
R1

##M2: fWhite
names(DNZV1_shore)
M2 <- glm(felev~
            fWhite +
            factor(StateNumLG) +
            factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(M2)

##testing for overdispersion
deviance(M2)/df.residual(M2)

##testing for multicollinearity
M2_Vif <- car::vif(M2) 
M2_Vif

#exponentiating coeff for odds ratios
M2Exp <- M2
M2Exp$coefficients <- exp(M2Exp$coefficients)
M2Exp

# pseudo R-squared
R2 <- (1-(M2$deviance)/(M2$null.deviance))
R2 <- round(R2,2)
R2

##M4: count_fema_sfha_W_1k
names(DNZV1_shore)
M4 <- glm(felev~
            count_fema_sfha_W_1k +
            factor(StateNumLG) +
            factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(M4)

##testing for overdispersion
deviance(M4)/df.residual(M4)

##testing for multicollinearity
M4_Vif <- car::vif(M4) 
M4_Vif

#exponentiating coeff for odds ratios
M4Exp <- M4
M4Exp$coefficients <- exp(M4Exp$coefficients)
M4Exp

# pseudo R-squared
R4 <- (1-(M4$deviance)/(M4$null.deviance))
R4 <- round(R4,2)
R4


##M5: NFIP_ICCadj_YOLZ_W_1M
names(DNZV1_shore)
M5 <- glm(felev~
            NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(M5)

##testing for overdispersion
deviance(M5)/df.residual(M5)

##testing for multicollinearity
M5_Vif <- car::vif(M5) 
M5_Vif

#exponentiating coeff for odds ratios
M5Exp <- M5
M5Exp$coefficients <- exp(M5Exp$coefficients)
M5Exp

# pseudo R-squared
R5 <- (1-(M5$deviance)/(M5$null.deviance))
R5 <- round(R5,2)
R5



#Model All
V1 <- stargazer(M0,M1,M2,M4,M5,
                type="html",
                omit=c("StateNumLG","fyDeclared"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison: Single Variable Model \n Shore Sample", 
                dep.var.labels = c("odds Ratio of felev"),
                add.lines = list(c("State FE","YES","YES","YES","YES","YES"),
                                 c("Year FE", "YES","YES","YES","YES","YES"),
                                 c("Pseudo $R2$", R0,R1,R2,R4,R5)),
                digits=2,
                column.sep.width = "10pt",
                #order=order,
                single.row = FALSE,
                align=TRUE,
                out="C:/Users/lgero/Box/Research/FEMA_project/Results/myHMA10/DNZ_V1/felev/zs_M1SW_fe_singleVarModels.htm")
```

```{r echo=FALSE, results= 'asis'}
stargazer(M0,M1,M2,M4,M5,
                type="html",
                omit=c("fyDeclared", "StateNumLG"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison: Single Variable Model \n Shore Sample", 
                dep.var.labels = c("odds Ratio of felev"),
                add.lines = list(c("State FE","YES","YES","YES","YES","YES"),
                                 c("Year FE", "YES","YES","YES","YES","YES"),
                                 c("Pseudo $R2$", R0,R1,R2,R4,R5)),
                covariate.labels = c("MHV ($100k W)",
                                     "Fraction White",
                                     "Count of HUs in FEMA SFHA 1k (W)",
                                     "NFIP ICC Claims 1M (W) by ZCTA-YOL"),
                digits=2,
                column.sep.width = "10pt",
                single.row = FALSE,
                align=TRUE)
```



##### M1 Series A.1 (Starting with best model from above and dropping vars)
```{r include= FALSE}
##M1: All vars included in stepwise model
M1 <- glm(felev ~  
             MHVadj_W_100k +
             fWhite +
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)

##testing for overdispersion
deviance(M1)/df.residual(M1) #

##testing for multicollinearity
M1_Vif <- car::vif(M1) ## 
M1_Vif

#exponentiating coeff for odds ratios
M1Exp <- M1
M1Exp$coefficients <- exp(M1Exp$coefficients)
M1Exp

# pseudo R-squared
R1 <- (1-(M1$deviance)/(M1$null.deviance))
R1 <- round(R1,2)
R1


##M2: dropping MHV
M2 <- glm(felev ~  
             #MHVadj_W_100k +
             fWhite +
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)

##testing for overdispersion
deviance(M2)/df.residual(M2) #

##testing for multicollinearity
M2_Vif <- car::vif(M2) ## 
M2_Vif

#exponentiating coeff for odds ratios
M2Exp <- M2
M2Exp$coefficients <- exp(M2Exp$coefficients)
M2Exp

# pseudo R-squared
R2 <- (1-(M2$deviance)/(M2$null.deviance))
R2 <- round(R2,2)
R2


##M3: dropping mrp_ideology1
M3 <- glm(felev ~  
             MHVadj_W_100k +
             #fWhite +
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)

summary(M3)

##testing for overdispersion
deviance(M3)/df.residual(M3) #

##testing for multicollinearity
M3_Vif <- car::vif(M3) ## 
M3_Vif

#exponentiating coeff for odds ratios
M3Exp <- M3
M3Exp$coefficients <- exp(M3Exp$coefficients)
M3Exp

# pseudo R-squared
R3 <- (1-(M3$deviance)/(M3$null.deviance))
R3 <- round(R3,2)
R3


##M4: dropping count_fema_sfha_W_1k
M4 <- glm(felev ~  
             MHVadj_W_100k +
             fWhite +
             #count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)
summary(M4)

##testing for overdispersion
deviance(M4)/df.residual(M4) #

##testing for multicollinearity
M4_Vif <- car::vif(M4) ## 
M4_Vif

#exponentiating coeff for odds ratios
M4Exp <- M4
M4Exp$coefficients <- exp(M4Exp$coefficients)
M4Exp

# pseudo R-squared
R4 <- (1-(M4$deviance)/(M4$null.deviance))
R4 <- round(R4,2)
R4


##M5: dropping NFIP_ICCadj_YOLZ_W_1M
M5 <-  glm(felev ~  
             MHVadj_W_100k +
             fWhite +
             count_fema_sfha_W_1k +
             #NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)
summary(M5)

##testing for overdispersion
deviance(M5)/df.residual(M5) #

##testing for multicollinearity
M5_Vif <- car::vif(M5) ## 
M5_Vif

#exponentiating coeff for odds ratios
M5Exp <- M5
M5Exp$coefficients <- exp(M5Exp$coefficients)
M5Exp

# pseudo R-squared
R5 <- (1-(M5$deviance)/(M5$null.deviance))
R5 <- round(R5,2)
R5




#Model All
V1 <- stargazer(M1,M2,M3,M4,M5, type="html",
                omit=c("StateNumLG","fyDeclared"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison", 
                dep.var.labels = c("Odds Ratio of felev"),
                add.lines = list(c("State FE","YES", "YES", "YES", "YES","YES","YES"),
                                 c("Year FE", "YES", "YES", "YES", "YES","YES","YES"),
                                 c("Pseudo $R2$", R1,R2,R3,R4,R5)),
                digits=2,
                column.sep.width = "10pt",
                #order=order,
                single.row = FALSE,
                align=TRUE,
                out="C:/Users/lgero/Box/Research/FEMA_project/Results/myHMA10/DNZ_V1/felev/zs_M1SW_fe_dropVars.htm")
```

```{r echo=FALSE, results= 'asis'}
stargazer(M1,M2,M3,M4,M5,type="html",
                omit=c("fyDeclared", "StateNumLG"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison: Full Sample, Dropping variables", 
                dep.var.labels = c("Odds Ratio of felev"),
                add.lines = list(c("State FE",  "YES", "YES", "YES","YES", "YES"),
                                 c("Year FE",  "YES", "YES", "YES","YES", "YES"),
                                 c("Pseudo $R2$",  R1,R2,R3,R4,R5)),
                covariate.labels = c("MHV ($100k W)",
                                     "Fraction White",
                                     "Count of HUs in FEMA SFHA 1k (W)",
                                     "NFIP ICC Claims 1M (W) by ZCTA-YOL"),
                digits=2,
                column.sep.width = "10pt",
                single.row = FALSE,
                align=TRUE)
```
The model above confirms that the stepwise process selected the model with the lowest AIC


##### Post Tests M1
```{r include = FALSE}
##M1: All vars included in the final stepwise model
M1 <- glm(felev ~  
             MHVadj_W_100k +
             fWhite +
             count_fema_sfha_W_1k +
             #NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore, family = binomial)
  
```


##### Examining outliers and leverage points
###### Diagnostics:
```{r echo=FALSE, message=FALSE, warning=FALSE}
par(mfrow=c(2,2))
plot(M1) #note that 1405 and 427, appear to be outliers

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

#following R in Action p. 305
# Set up a 2 by 2 plotting area
par(mfrow = c(2, 2))

# Plot 1: Predicted values vs. deviance residuals
plot(predict(M1, type = "response"),
     residuals(M1, type = "deviance"),
     main = "Predicted vs. Deviance Residuals",
     xlab = "Predicted Values",
     ylab = "Deviance Residuals")

# Plot 2: Hat values
plot(hatvalues(M1),
     main = "Hat Values",
     xlab = "Index",
     ylab = "Hat Values")

# Plot 3: Studentized residuals
plot(rstudent(M1),
     main = "Studentized Residuals",
     xlab = "Index",
     ylab = "Studentized Residuals")

# Plot 4: Cook's distance
plot(cooks.distance(M1),
     main = "Cook's Distance",
     xlab = "Index",
     ylab = "Cook's Distance")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Identifying outliers
#from book p.194
outlierTest(M1) #note that 427 is identified as outliers

```

```{r include= FALSE}
hat.plot <- function(M1) {
  p <- length(coefficients(M1))
  n <- length(fitted(M1))
  plot(hatvalues(M1), main="Index Plot of Hat Values")
  abline(h=c(2,3)*p/n, col="red", lty=2)
  identify(1:n, hatvalues(M1), names(hatvalues(M1)))
  
}

#hat.plot(M1) #getting issue here
```

######Identifying influential observations 
```{r echo=FALSE, message=FALSE, warning=FALSE}
#following (p.196)
cutoff <- 4/(nrow(DNZV1_shore)-length(M1$coefficients)-2)
plot(M1, which=4, cook.levels=cutoff)
abline(h=cutoff, lty=2, col="red")  #

#assessing impact of influential observations on vars
library(car)
#avPlots(M1, ask=FALSE, id.method="identify") This takes time. Identifies similar DNZs

#influence plots
influencePlot(M1) #

#examining the rows that are identifies as outliers or leverage points 
seeLev <- DNZV1_shore[c(24,339,3463,4397),]


```


### M1_Unlev: Dropping leverage points and rerunning model 
```{r include= FALSE}
DNZV1_shore_unLev <- DNZV1_shore[-c(4, 24, 427, 1405, 4338, 1583), ]

M1_unlev <-  glm(felev ~  
             MHVadj_W_100k +
             fWhite +
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore_unLev , family = binomial)
summary(M1_unlev)


##testing for overdispersion
deviance(M1_unlev)/df.residual(M1_unlev)

##testing for multicollinearity
M1_unlev_Vif <- car::vif(M1_unlev) #not this includes fixed effects
M1_unlev_Vif

#exponentiating coeff for odds ratios
M1_unlevExp <- M1_unlev
M1_unlevExp$coefficients <- exp(M1_unlevExp$coefficients)
M1_unlevExp

# pseudo R-squared
R1 <- (1-(M1_unlev$deviance)/(M1_unlev$null.deviance))
R1 <- round(R1,2)
R1

##Model All
V1 <- stargazer(M1_unlev,
                type="html",
                omit=c("StateNumLG","fyDeclared"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison", 
                dep.var.labels = c("Ratio of felev"),
                add.lines = list(c("State FE","Yes"),
                                 c("Year FE", "Yes"),
                                 c("Pseudo $R2$", R1)),
                digits=2,
                column.sep.width = "10pt",
                #order=order,
                single.row = FALSE,
                align=TRUE,
                out="C:/Users/lgero/Box/Research/FEMA_project/Results/myHMA10/DNZ_V1/felev/zs_M1SW_unlev_fe.htm")


```


```{r echo=FALSE, results= 'asis'}
stargazer(M1_unlev, 
          type="html",
                omit=c("fyDeclared", "StateNumLG"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison: Dropping Influential Observations", 
                dep.var.labels = c("Odds Ratio of felev"),
                add.lines = list(c("State FE","Yes"),
                                 c("Year FE", "Yes"),
                                 c("Pseudo $R2$", R1)),
                covariate.labels = c("MHV ($100k W)",
                                     "Fraction White",
                                     "Count of HUs in FEMA SFHA 1k (W)",
                                     "NFIP ICC Claims 1M (W) by ZCTA-YOL"),
                digits=2,
                column.sep.width = "10pt",
                single.row = FALSE,
                align=TRUE)
```

##### Post Tests M1_unLev
```{r include = FALSE}
##M1: All vars included in the final stepwise model

M1<-  glm(felev ~  
             MHVadj_W_100k +
             fWhite +
             count_fema_sfha_W_1k +
             NFIP_ICCadj_YOLZ_W_1M +
            factor(StateNumLG) +
            factor(fyDeclared), 
            data = DNZV1_shore_unLev , family = binomial)

summary(M1)
```


##### Examining outliers and leverage points

###### Diagnostics
```{r echo=FALSE, message=FALSE, warning=FALSE}
par(mfrow=c(2,2))
plot(M1) #

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

#following R in Action p. 305
# Set up a 2 by 2 plotting area
par(mfrow = c(2, 2))

# Plot 1: Predicted values vs. deviance residuals
plot(predict(M1, type = "response"),
     residuals(M1, type = "deviance"),
     main = "Predicted vs. Deviance Residuals",
     xlab = "Predicted Values",
     ylab = "Deviance Residuals")

# Plot 2: Hat values
plot(hatvalues(M1),
     main = "Hat Values",
     xlab = "Index",
     ylab = "Hat Values")

# Plot 3: Studentized residuals
plot(rstudent(M1),
     main = "Studentized Residuals",
     xlab = "Index",
     ylab = "Studentized Residuals")

# Plot 4: Cook's distance
plot(cooks.distance(M1),
     main = "Cook's Distance",
     xlab = "Index",
     ylab = "Cook's Distance")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
#Identifying outliers
#from book p.194
outlierTest(M1) #

```

```{r include= FALSE}
hat.plot <- function(M1) {
  p <- length(coefficients(M1))
  n <- length(fitted(M1))
  plot(hatvalues(M1), main="Index Plot of Hat Values")
  abline(h=c(2,3)*p/n, col="red", lty=2)
  identify(1:n, hatvalues(M1), names(hatvalues(M1)))
  
}

#hat.plot(M1) #getting issue here
```

######Identifying influential observations 
```{r echo=FALSE, message=FALSE, warning=FALSE}
#identifying influential observations (p.196)
cutoff <- 4/(nrow(DNZV1_shore_unLev)-length(M1$coefficients)-2)
plot(M1, which=4, cook.levels=cutoff)
abline(h=cutoff, lty=2, col="red")

#assessing impact of influential observations on vars
library(car)
#avPlots(M1, ask=FALSE, id.method="identify") This takes time. Identifies similar DNZs

#influence plots
influencePlot(M1) #identifies 


```

###### Drawing predicted probabilities 
```{r include= FALSE}
#following: https://www.bing.com/videos/riverview/relatedvideo?&q=logistic+regression+in+r&&mid=B29E2A8DFA23C6D477A5B29E2A8DFA23C6D477A5&&FORM=VRDGAR
predicted.data.M1 <- data.frame(probability.of.elev=M1$fitted.values,
                              felev=DNZV1_shore_unLev)

#sorting from low to high
predicted.data.M1 <- predicted.data.M1[
  order(predicted.data.M1$probability.of.elev, decreasing=FALSE),]

#add a new column to the data.frame that has the rank of each sample, from low probability to high probability
predicted.data.M1$rank <- 1:nrow(predicted.data.M1)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#draw data
ggplot(data=predicted.data.M1, aes(x=rank, y=probability.of.elev))+
  geom_point(aes(color=probability.of.elev), alpha=1, shape= 4, stroke =2)+
  xlab("Index")+
  ylab("Predicted probability of Elevation")
```



#####
```{r include= FALSE}
path1 <- ("C:/Users/lgero/Box/Research/FEMA_project/Data/Edited/HMA/DNZLevel/DNZ_V1/")
write.csv(DNZV1_shore_unLev, file.path(path1, "DNZV1_shore_unLev.csv"), row.names=TRUE)

```




#### Logistic model comparing original Dissertation model with SVSS predictors 
```{r include = FALSE}
##Dis_M1: All + Baseline (w year FEs)
names(DNZV1_shore)
Dis_M1 <- glm(felev~
                MHVadj_W_100k +
                fWhite +
                RepRate +
                ZCTA_shore +
                count_fema_sfha_W_1k +
                IHP_fldDamAmountAdjDNZ_W_10M +
                TotPop_W_10k +
                factor(StateNumLG) +
                factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(Dis_M1)

##testing for overdispersion
deviance(Dis_M1)/df.residual(Dis_M1) #0.52

##testing for multicollinearity
#Dis_M1_Vif <- car::vif(Dis_M1) #
#Dis_M1_Vif

#exponentiating coeff for odds ratios
Dis_M1Exp <- Dis_M1
Dis_M1Exp$coefficients <- exp(Dis_M1Exp$coefficients)
Dis_M1Exp

# pseudo R-squared
Dis_R1 <- (1-(Dis_M1$deviance)/(Dis_M1$null.deviance))
Dis_R1 <- round(Dis_R1,2)
Dis_R1


##SVSS_M1: All + Baseline (w year FEs)
names(DNZV1_shore)
SVSS_M1 <- glm(felev~
            fWhite +
            MHVadj_W_100k +
            #mrp_ideology1 +
            TaxBaseEst_1B_W +
            ZCTA_shore +
            NFIP_ICCadj_YOLZ_W_1M +
            count_fema_sfha_W_1k +
            Hurricane +
            factor(StateNumLG) +
            factor(fyDeclared),
          data=DNZV1_shore,family=binomial(link = "logit"))
summary(SVSS_M1)

##testing for overdispersion
deviance(SVSS_M1)/df.residual(SVSS_M1) #0.52

##testing for multicollinearity
#SVSS_M1_Vif <- car::vif(SVSS_M1) #
#SVSS_M1_Vif

#exponentiating coeff for odds ratios
SVSS_M1Exp <- SVSS_M1
SVSS_M1Exp$coefficients <- exp(SVSS_M1Exp$coefficients)
SVSS_M1Exp

# pseudo R-squared
SVSS_R1 <- (1-(SVSS_M1$deviance)/(SVSS_M1$null.deviance))
SVSS_R1 <- round(SVSS_R1,2)
SVSS_R1

##Model All
V1 <- stargazer(Dis_M1, SVSS_M1,
                type="html",
                omit=c("StateNumLG","fyDeclared"),
                apply.coef=exp,
                apply.ci=exp,
                t.auto=F,
                p.auto=F,
                title="Logit Model Comparison", 
                dep.var.labels = c("Ratio of felev"),
                add.lines = list(c("State FE","Yes", "Yes"),
                                 c("Year FE", "Yes", "Yes"),
                                 c("Pseudo $R2$", Dis_R1, SVSS_R1)),
                digits=2,
                column.sep.width = "10pt",
                #order=order,
                single.row = FALSE,
                align=TRUE,
                out="C:/Users/lgero/Box/Research/FEMA_project/Results/myHMA10/DNZ_V1/felev/fs_dis_svss_fe.htm")

```



