

---
title: "Supplementary Information: Descriptive Statistics"
author: "Laura Geronimo"
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float: true
    number_sections: true
    theme: "default"

---

## Notes


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
getwd()

##Libraries
library(dplyr)
library(stringr)
library(Hmisc)
library(tidycensus)
library(corrplot)
library(dplyr)
library(data.table)
library(ggplot2)
library(pastecs)
library(car)
library(gvlma)
library(qcc)
library(stargazer)
library(viridis)

library(forcats)
library(boot)
library(lmtest)
library(sandwich)
library(ggpubr)

options (scipen=999)

#importing data
DNZV1 <- read.csv('C:/Users/lgero/Box/Research/FEMA_project/Data/Edited/HMA/DNZLevel/DNZ_V1/DNZ_V1.csv')

names(DNZV1)
DNZV1 <- DNZV1[,c(-1)]
DNZV1_shore <- subset(DNZV1, ZCTA_shore==1)

#Elevation subsets
DNZV1E <- subset(DNZV1, Elev>0)
DNZV1E_shore <- subset(DNZV1E, ZCTA_shore==1)
DNZV1E_sandy <- subset(DNZV1E, namedStorm=="sandy")
DNZV1E_hurricane <- DNZV1E %>%
  filter(!is.na(HurricaneName))

#Acquisition subsets
DNZV1A <- subset(DNZV1, Acqui>0)
DNZV1A_shore <- subset(DNZV1A, ZCTA_shore==1)
DNZV1A_sandy <- subset(DNZV1A, namedStorm=="sandy")

```

#All DNZs

## Heatmap: felev by deciles of fWhite and MHV
```{r include=FALSE}

# Create deciles for MHVadj_100k and fWhite
DNZV1$MHVadj_100k_decile <- cut(DNZV1$MHVadj_100k, breaks=quantile(DNZV1$MHVadj_100k, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1$fWhite_decile <- cut(DNZV1$fWhite, breaks=quantile(DNZV1$fWhite, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ MHVadj_100k_decile + fWhite_decile, data=DNZV1, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("MHVadj_100k_decile", "fWhite_decile"))

# Create the heatmap
F1 <- ggplot(pivot_table_melt, aes(x=fWhite_decile, y=MHVadj_100k_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="Race by MHV", x="Deciles of fWhite", y="Deciles of MHVadj_100k", fill="felev") +
  theme_minimal()
```


## Heatmap: felev by deciles of MHV & MRP ideology
```{r include=FALSE}

# Create deciles for MHVadj_100k and mrp_ideology1
DNZV1$MHVadj_100k_decile <- cut(DNZV1$MHVadj_100k, breaks=quantile(DNZV1$MHVadj_100k, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1$mrp_ideology1_decile <- cut(DNZV1$mrp_ideology1, breaks=quantile(DNZV1$mrp_ideology1, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ MHVadj_100k_decile + mrp_ideology1_decile, data=DNZV1, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("MHVadj_100k_decile", "mrp_ideology1_decile"))

# Create the heatmap
F2 <- ggplot(pivot_table_melt, aes(x=mrp_ideology1_decile, y=MHVadj_100k_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="MHV by Political Ideology", x="Deciles of mrp_ideology1", y="Deciles of MHVadj_100k", fill="felev") +
  theme_minimal()
```


## Heatmap: felev by deciles of fWhite & MRP ideology
```{r include=FALSE}

# Create deciles for fWhite and mrp_ideology1
DNZV1$fWhite_decile <- cut(DNZV1$fWhite, breaks=quantile(DNZV1$fWhite, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1$mrp_ideology1_decile <- cut(DNZV1$mrp_ideology1, breaks=quantile(DNZV1$mrp_ideology1, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ fWhite_decile + mrp_ideology1_decile, data=DNZV1, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("fWhite_decile", "mrp_ideology1_decile"))

# Create the heatmap
F3 <- ggplot(pivot_table_melt, aes(x=mrp_ideology1_decile, y=fWhite_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="Race by Political Ideology", x="Deciles of mrp_ideology1", y="Deciles of fWhite", fill="felev") +
  theme_minimal()

library(gridExtra)
grid.arrange(F1,F2,F3, ncol=3)
```



## Heatmap: felev by deciles of MHV & RepRate
```{r include=FALSE}

# Create deciles for MHVadj_100k and RepRate
DNZV1$MHVadj_100k_decile <- cut(DNZV1$MHVadj_100k, breaks=quantile(DNZV1$MHVadj_100k, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1$RepRate_decile <- cut(DNZV1$RepRate, breaks=quantile(DNZV1$RepRate, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ MHVadj_100k_decile + RepRate_decile, data=DNZV1, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("MHVadj_100k_decile", "RepRate_decile"))

# Create the heatmap
F4 <- ggplot(pivot_table_melt, aes(x=RepRate_decile, y=MHVadj_100k_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="MHV by Political Ideology", x="Deciles of RepRate", y="Deciles of MHVadj_100k", fill="felev") +
  theme_minimal()
```


## Heatmap: felev by deciles of fWhite & RepRate
```{r include=FALSE}

# Create deciles for fWhite and RepRate
DNZV1$fWhite_decile <- cut(DNZV1$fWhite, breaks=quantile(DNZV1$fWhite, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1$RepRate_decile <- cut(DNZV1$RepRate, breaks=quantile(DNZV1$RepRate, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ fWhite_decile + RepRate_decile, data=DNZV1, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("fWhite_decile", "RepRate_decile"))

# Create the heatmap
F5 <- ggplot(pivot_table_melt, aes(x=RepRate_decile, y=fWhite_decile, fill=value)) +
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="Race by Political Ideology", x="Deciles of RepRate", y="Deciles of fWhite", fill="felev") +
  theme_minimal()

library(gridExtra)
grid.arrange(F1,F4,F5, ncol=3)
```

##Heatmap by state - full sample
```{r include=FALSE}
# Create deciles for MHVadj_100k and fWhite
DNZV1$MHVadj_100k_decile <- cut(DNZV1$MHVadj_100k, breaks=quantile(DNZV1$MHVadj_100k, probs=seq(0, 1, 0.1), na.rm=TRUE), include.lowest=TRUE, labels=FALSE)
DNZV1$fWhite_decile <- cut(DNZV1$fWhite, breaks=quantile(DNZV1$fWhite, probs=seq(0, 1, 0.1), na.rm=TRUE), include.lowest=TRUE, labels=FALSE)

# Create a pivot table including p2state
pivot_table <- DNZV1 %>%
  group_by(p2state, MHVadj_100k_decile, fWhite_decile) %>%
  summarise(felev = mean(felev, na.rm=TRUE)) %>%
  ungroup()

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("p2state", "MHVadj_100k_decile", "fWhite_decile"))

# Create the heatmap with facet wrap
F1 <- ggplot(pivot_table_melt, aes(x=fWhite_decile, y=MHVadj_100k_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="Race by MHV", x="Deciles of fWhite", y="Deciles of MHVadj_100k", fill="felev") +
  theme_minimal() +
  facet_wrap(~ p2state, scales = "free")

# Print the heatmap
F1
```

#Shoreline DNZs
## Heatmap: felev by deciles of fWhite and MHV
```{r include=FALSE}

# Create deciles for MHVadj_100k and fWhite
DNZV1_shore2$MHVadj_100k_decile <- cut(DNZV1_shore2$MHVadj_100k, breaks=quantile(DNZV1_shore2$MHVadj_100k, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1_shore2$fWhite_decile <- cut(DNZV1_shore2$fWhite, breaks=quantile(DNZV1_shore2$fWhite, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ MHVadj_100k_decile + fWhite_decile, data=DNZV1_shore2, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("MHVadj_100k_decile", "fWhite_decile"))

# Create the heatmap
F1 <- ggplot(pivot_table_melt, aes(x=fWhite_decile, y=MHVadj_100k_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="Race by MHV", x="Deciles of fWhite", y="Deciles of MHVadj_100k", fill="felev") +
  theme_minimal()
```


## Heatmap: felev by deciles of MHV & MRP ideology
```{r include=FALSE}

# Create deciles for MHVadj_100k and mrp_ideology1
DNZV1_shore2$MHVadj_100k_decile <- cut(DNZV1_shore2$MHVadj_100k, breaks=quantile(DNZV1_shore2$MHVadj_100k, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1_shore2$mrp_ideology1_decile <- cut(DNZV1_shore2$mrp_ideology1, breaks=quantile(DNZV1_shore2$mrp_ideology1, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ MHVadj_100k_decile + mrp_ideology1_decile, data=DNZV1_shore2, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("MHVadj_100k_decile", "mrp_ideology1_decile"))

# Create the heatmap
F2 <- ggplot(pivot_table_melt, aes(x=mrp_ideology1_decile, y=MHVadj_100k_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="MHV by Political Ideology", x="Deciles of mrp_ideology1", y="Deciles of MHVadj_100k", fill="felev") +
  theme_minimal()
```


## Heatmap: felev by deciles of fWhite & MRP ideology
```{r include=FALSE}

# Create deciles for fWhite and mrp_ideology1
DNZV1_shore2$fWhite_decile <- cut(DNZV1_shore2$fWhite, breaks=quantile(DNZV1_shore2$fWhite, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)
DNZV1_shore2$mrp_ideology1_decile <- cut(DNZV1_shore2$mrp_ideology1, breaks=quantile(DNZV1_shore2$mrp_ideology1, probs=seq(0, 1, 0.1)), include.lowest=TRUE, labels=FALSE)

# Create a pivot table
pivot_table <- aggregate(felev ~ fWhite_decile + mrp_ideology1_decile, data=DNZV1_shore2, mean)

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("fWhite_decile", "mrp_ideology1_decile"))

# Create the heatmap
F3 <- ggplot(pivot_table_melt, aes(x=mrp_ideology1_decile, y=fWhite_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="Race by Political Ideology", x="Deciles of mrp_ideology1", y="Deciles of fWhite", fill="felev") +
  theme_minimal()

library(gridExtra)
grid.arrange(F1,F2,F3, ncol=3)
```


##Heatmap by state - shore sample
```{r include=FALSE}
DNZV1_shore2 <- subset(DNZV1_shore, p2state!="Illinois" &
                         p2state!="Indiana" & 
                         p2state!="Kentucky" & 
                         p2state!="Ohio" &
                         p2state!="West Virginia")

# Create deciles for MHVadj_100k and fWhite
DNZV1_shore2$MHVadj_100k_decile <- cut(DNZV1_shore2$MHVadj_100k, breaks=quantile(DNZV1_shore2$MHVadj_100k, probs=seq(0, 1, 0.1), na.rm=TRUE), include.lowest=TRUE, labels=FALSE)
DNZV1_shore2$fWhite_decile <- cut(DNZV1_shore2$fWhite, breaks=quantile(DNZV1_shore2$fWhite, probs=seq(0, 1, 0.1), na.rm=TRUE), include.lowest=TRUE, labels=FALSE)

# Create a pivot table including p2state
pivot_table <- DNZV1_shore2 %>%
  group_by(p2state, MHVadj_100k_decile, fWhite_decile) %>%
  summarise(felev = mean(felev, na.rm=TRUE)) %>%
  ungroup()

# Reshape the data for ggplot
pivot_table_melt <- melt(pivot_table, id.vars=c("p2state", "MHVadj_100k_decile", "fWhite_decile"))

# Create the heatmap with facet wrap
F1 <- ggplot(pivot_table_melt, aes(x=fWhite_decile, y=MHVadj_100k_decile, fill=value)) + 
  geom_tile() + 
  scale_fill_gradient(low="blue", high="red") + 
  labs(title="Race by MHV", x="Deciles of fWhite", y="Deciles of MHVadj_100k", fill="felev") +
  theme_minimal() +
  facet_wrap(~ p2state, scales = "free")

# Print the heatmap
F1
```




#All DNZs
## felev
###State level analysis
####Mean felev by fWhite_dec by state
```{r include= FALSE}
# Calculate deciles of fWhite for each p2state
DNZV1 <- DNZV1 %>%
  group_by(p2state) %>%
  mutate(fWhite_decile = ntile(fWhite, 10))

# Compute mean of Elev within each decile for each p2state
mean_felev_data <- DNZV1 %>%
  group_by(p2state, fWhite_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x = fWhite_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ p2state) +
  labs(title = "Mean felev by Deciles of fWhite for each p2State",
       x = "Deciles of fWhite",
       y = "Mean felev") +
  theme_minimal()
```

####Mean felev by MHVadj_100k_dec by state
```{r include= FALSE}
# Calculate deciles of MHVadj_100k for each p2state
DNZV1 <- DNZV1 %>%
  group_by(p2state) %>%
  mutate(MHVadj_100k_decile = ntile(MHVadj_100k, 10))

# Compute mean of Elev within each decile for each p2state
mean_felev_data <- DNZV1 %>%
  group_by(p2state, MHVadj_100k_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x = MHVadj_100k_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ p2state) +
  labs(title = "Mean felev by Deciles of MHVadj_100k for each State",
       x = "Deciles of MHVadj_100k",
       y = "Mean felev") +
  theme_minimal()
```

####Mean felev by mrp_ideology_dec by state
```{r include= FALSE}
# Calculate deciles ofmrp_ideology for each p2state
DNZV1 <- DNZV1 %>%
  group_by(p2state) %>%
  mutate(mrp_ideology_decile = ntile(mrp_ideology, 10))

# Compute mean of Elev within each decile for each p2state
mean_felev_data <- DNZV1 %>%
  group_by(p2state,mrp_ideology_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x =mrp_ideology_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ p2state) +
  labs(title = "Mean felev by Deciles of mrp_ideology for each State",
       x = "Deciles of mrp_ideology",
       y = "Mean felev") +
  theme_minimal()
```

#Shore DNZs
## felev
###State level analysis
####Mean felev by fWhite_dec by state
```{r include= FALSE}
# Calculate deciles of fWhite for each p2state
DNZV1_shore <- DNZV1_shore %>%
  group_by(p2state) %>%
  mutate(fWhite_decile = ntile(fWhite, 10))

# Compute mean of Elev within each decile for each p2state
mean_felev_data <- DNZV1_shore %>%
  group_by(p2state, fWhite_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x = fWhite_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ p2state) +
  labs(title = "Mean felev by Deciles of fWhite for each p2State",
       x = "Deciles of fWhite",
       y = "Mean felev") +
  theme_minimal()
```

####Mean felev by MHVadj_100k_dec by state
```{r include= FALSE}
# Calculate deciles of MHVadj_100k for each p2state
DNZV1_shore <- DNZV1_shore %>%
  group_by(p2state) %>%
  mutate(MHVadj_100k_decile = ntile(MHVadj_100k, 10))

# Compute mean of Elev within each decile for each p2state
mean_felev_data <- DNZV1_shore %>%
  group_by(p2state, MHVadj_100k_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x = MHVadj_100k_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ p2state) +
  labs(title = "Mean felev by Deciles of MHVadj_100k for each State",
       x = "Deciles of MHVadj_100k",
       y = "Mean felev") +
  theme_minimal()
```

####Mean felev by mrp_ideology_dec by state
```{r include= FALSE}
# Calculate deciles ofmrp_ideology for each p2state
DNZV1_shore <- DNZV1_shore %>%
  group_by(p2state) %>%
  mutate(mrp_ideology_decile = ntile(mrp_ideology, 10))

# Compute mean of Elev within each decile for each p2state
mean_felev_data <- DNZV1_shore %>%
  group_by(p2state,mrp_ideology_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x =mrp_ideology_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ p2state) +
  labs(title = "Mean felev by Deciles of mrp_ideology for each State",
       x = "Deciles of mrp_ideology",
       y = "Mean felev") +
  theme_minimal()
```




##GOT HERE ####

#NOTE: Hurricanes need work

### Hurricane level analysis
####Mean flev by fWhite_dec by hurricane
```{r include= FALSE}
DNZV1_hurr<- DNZV1_hurr %>%
  filter(!is.na(HurricaneName))

# Calculate deciles of fWhite for each HurricaneName
DNZV1_hurr <- DNZV1_hurr %>%
  group_by(HurricaneName) %>%
  mutate(fWhite_decile = ntile(fWhite, 10))

# Compute mean of Elev within each decile for each HurricaneName
mean_felev_data <- DNZV1_hurr %>%
  group_by(HurricaneName, fWhite_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x = fWhite_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ HurricaneName) +
  labs(title = "Mean felev by Deciles of fWhite for each HurricaneName",
       x = "Deciles of fWhite",
       y = "Mean felev") +
  theme_minimal()
```

####Mean felev by MHVadj_100k_dec by hurricane
```{r include= FALSE}
# Calculate deciles of MHVadj_100k for each HurricaneName
DNZV1_hurr <- DNZV1_hurr %>%
  group_by(HurricaneName) %>%
  mutate(MHVadj_100k_decile = ntile(MHVadj_100k, 10))

# Compute mean of Elev within each decile for each HurricaneName
mean_felev_data <- DNZV1_hurr %>%
  group_by(HurricaneName, MHVadj_100k_decile) %>%
  summarise(
    mean_felev = mean(felev, na.rm = TRUE),
    sem_felev = sd(felev, na.rm = TRUE) / sqrt(n())
  ) %>%
  ungroup()

# Create the plot using facet_wrap
ggplot(mean_felev_data, aes(x = MHVadj_100k_decile, y = mean_felev)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_felev - sem_felev, ymax = mean_felev + sem_felev), width = 0.2) +
  facet_wrap(~ HurricaneName) +
  labs(title = "Mean felev by Deciles of MHVadj_100k for each State",
       x = "Deciles of MHVadj_100k",
       y = "Mean felev") +
  theme_minimal()
```

